Dewlap color variation in \textit{Anolis sagrei} is maintained among habitats within islands of the West Indies

### 2021-09-07 ms/main_title.tex
submitted

	\textsc{Rapha\"{e}l Scherrer}$^{1,3}$ \thanks{Corresponding author} (raphael.scherrer@evobio.eu, ORCID 0000-0002-1447-7630),\\
    \textsc{Colin M. Donihue}$^{1,4}$ (colindonihue@gmail.com, 0000-0003-1096-8536),\\
	\textsc{R. Graham Reynolds}$^2$ (greynold@unca.edu, 0000-0002-0056-8304),\\ 
    \textsc{Jonathan B. Losos}$^{1,4}$ (losos@wustl.edu, 0000-0003-4712-8258) and\\
	\textsc{Anthony J. Geneva}$^{1,5}$ (anthony.geneva@gmail.com, 0000-0001-8253-6527)\\[1ex]

@@

	\textbf{Running title} --- Dewlap coloration in \textit{Anolis sagrei}.

>>>>

	\textsc{Rapha\"{e}l Scherrer}$^{1,3}$ \thanks{Corresponding author} (raphael.scherrer@evobio.eu, ORCID 0000-0002-1447-7630),\\
    \textsc{Colin M. Donihue}$^{1,4}$ (colindonihue@gmail.com, 0000-0003-1096-8536),\\
	\textsc{R. Graham Reynolds}$^2$ (greynold@unca.edu, 0000-0002-0056-8304),\\ 
    \textsc{Jonathan B. Losos}$^{1,4}$ (losos@wustl.edu, 0000-0003-4712-8258) and\\
	\textsc{Anthony J. Geneva}$^{1,5}$ (anthony.geneva@rutgers.edu, 0000-0001-8253-6527)\\[1ex]

@@

	\section*{Running title}

	Dewlap coloration in \textit{Anolis sagrei}.

	\section*{Acknowledgements}

	\input{sections/acknowledgments.tex}

	\section*{Author Contributions}

	CMD, RGR, AJG and JBL designed the study. CMD, RGR and AJG organized the fieldwork and collected the data. RS performed the analyses and wrote the manuscript, under the supervision of CMD, RGR and AJG. All authors contributed to revisions of the manuscript. JBL provided the resources.\\

	The authors have no conflict of interest to declare.
